Capabilities, MMIO and Robust Safety

### 2020-03-31 capability-meetings-notes/10-03/main.tex
mmio meeting notes: \VR and \ER: fix the order of arguments (world goes first)

\[
  \VR^{\Psi}(p, g, b, e, a) \eqdef \underbrace{\ldots}_{\text{as before}} \ast \; \pure{\forall a' \in [b,e).\; \Psi(a')}
\]

@@

\newcommand{\Wpub}{\sqsupseteq^{\X{pub}}}
\newcommand{\Wpriv}{\sqsupseteq^{\X{priv}}}
\begin{mathpar}
  \mprset{vskip=0.5em}
  \inferrule
  { \forall a_{i} \in A_{\X{entry}} \ldotp\,
      \knowInv{\iota}{\exists t.\; \tracefrag{t} \ast P(t)}\!
         \vdash
         \forall W \ldotp\;(\ER^{\notMMIO} (\X{RX}, g, b, e, a_i))\spac W
       \\
     \\
    (r[\overline{r_{a_{i}} := (\X{E}, g, b, e, a_i)}], m, \emptyset) \longrightarrow^*
    (r', m', t)
  }
  {P(t)}
\end{mathpar}

@@

\begin{remark}
  Note that we could have written
  $\ldots \vdash \forall W \ldotp \; (\VR^{\notMMIO} (\X{E}, \ldots))\; W$ %)
  in the above theorem, instead of using the expression relation. This is
  equivalent, and easily unfolds to the former statement through the definition
  of the value relation. I wrote $\ER$ to place the focus on the execution of
  the driver being safe. I consider this a matter of taste.
\end{remark}

@@

\begin{mathpar}
  \mprset{vskip=0.5em}
  \inferrule
  { \forall a_{i} \in A_{\X{entry}} \ldotp\,\left\{
    {\begin{array}{ll}
    \knowInv{\iota}{\exists t.\; \tracefrag{t} \ast P(t)}\ast
    \driverC(b,e,\overline{\V{op}_l})\!
         \vdash \\
         \forall W \Wpriv \Winit \ldotp\;(\ER^{\notMMIO} (\X{RX}, g, b, e, a_i))\spac W
        \end{array}} \right. \\
   \initOKS{[b,e)}[r][m][\Winit] \\
  (r[\overline{r_{a_{i}} := (\X{E}, g, b, e, a_i)}], m, \emptyset) \longrightarrow^* (r', m', t)\\
  }
  {P(t)}
\end{mathpar}

@@

\begin{mathpar}
  \mprset{vskip=0.5em}
  \inferrule
  {  \forall a_{i} \in A_{\X{entry}} \ldotp\,\left\{
    {\begin{array}{ll}
    \knowInv{\iota}{\exists t.\; \tracefrag{t} \ast P(t)}\ast
    \driverC(b,e,\overline{\V{op}_l})\!
         \vdash \\
         \forall W \Wpriv \Winit \ldotp\;(\ER^{\notMMIO} (\X{RX}, g, b, e, a_i))\spac W
        \end{array}} \right. \\   \X{bootSpec}^{\X{sem}}(P,g,b,e,A_{\X{entry}}, \Winit) \\
  (r_0, m_0, \emptyset) \longrightarrow^* (r, m, t)\\
  }
  {P(t)}
\end{mathpar}

>>>>

\[
  \VR^{\Psi}(W)(p, g, b, e, a) \eqdef \underbrace{\ldots}_{\text{as before}} \ast \; \pure{\forall a' \in [b,e).\; \Psi(a')}
\]

@@

\newcommand{\Wpub}{\sqsupseteq^{\X{pub}}}
\newcommand{\Wpriv}{\sqsupseteq^{\X{priv}}}
\begin{mathpar}
  \mprset{vskip=0.5em}
  \inferrule
  { \forall a_{i} \in A_{\X{entry}} \ldotp\,
      \knowInv{\iota}{\exists t.\; \tracefrag{t} \ast P(t)}\!
         \vdash
         \forall W \ldotp\;\ER^{\notMMIO} (W) (\X{RX}, g, b, e, a_i)
       \\
     \\
    (r[\overline{r_{a_{i}} := (\X{E}, g, b, e, a_i)}], m, \emptyset) \longrightarrow^*
    (r', m', t)
  }
  {P(t)}
\end{mathpar}

@@

\begin{remark}
  Note that we could have written
  $\ldots \vdash \forall W \ldotp \; \VR^{\notMMIO} (W) (\X{E}, \ldots)$
  in the above theorem, instead of using the expression relation. This is
  equivalent, and easily unfolds to the former statement through the definition
  of the value relation. I wrote $\ER$ to place the focus on the execution of
  the driver being safe. I consider this a matter of taste.
\end{remark}

@@

\begin{mathpar}
  \mprset{vskip=0.5em}
  \inferrule
  { \forall a_{i} \in A_{\X{entry}} \ldotp\,\left\{
    {\begin{array}{ll}
    \knowInv{\iota}{\exists t.\; \tracefrag{t} \ast P(t)}\ast
    \driverC(b,e,\overline{\V{op}_l})\!
         \vdash \\
         \forall W \Wpriv \Winit \ldotp\;\ER^{\notMMIO} (W) (\X{RX}, g, b, e, a_i)
        \end{array}} \right. \\
   \initOKS{[b,e)}[r][m][\Winit] \\
  (r[\overline{r_{a_{i}} := (\X{E}, g, b, e, a_i)}], m, \emptyset) \longrightarrow^* (r', m', t)\\
  }
  {P(t)}
\end{mathpar}

@@

\begin{mathpar}
  \mprset{vskip=0.5em}
  \inferrule
  {  \forall a_{i} \in A_{\X{entry}} \ldotp\,\left\{
    {\begin{array}{ll}
    \knowInv{\iota}{\exists t.\; \tracefrag{t} \ast P(t)}\ast
    \driverC(b,e,\overline{\V{op}_l})\!
         \vdash \\
         \forall W \Wpriv \Winit \ldotp\;\ER^{\notMMIO} (W) (\X{RX}, g, b, e, a_i)
        \end{array}} \right. \\   \X{bootSpec}^{\X{sem}}(P,g,b,e,A_{\X{entry}}, \Winit) \\
  (r_0, m_0, \emptyset) \longrightarrow^* (r, m, t)\\
  }
  {P(t)}
\end{mathpar}
